Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module

### 2025-10-23 bv-triples-intro.tex
Slides complete.

%----------------------------------------------------+
\begin{frame}[fragile]{Keywords}
\tikzstyle{every picture}+=[remember picture]
	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<5->{
			\tikz[baseline]{
		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
		            {...};
			}
		}
	\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<4->{
			 \tikz[baseline]{
		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
		            {...};
			}
		}
	\end{column}
	\end{columns}

@@

	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<3->{
	 		 \tikz[baseline]{
	            \node[draw=green!40,anchor=base,text width=5cm] (s3)
	            {...};
	         }
		}		   	
		\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<2->{
				\tikz[baseline]{
	            \node[draw=red!40,anchor=base,text width=5cm] (s4)
	            {...};
	           }	
			}
		\end{column}
	\end{columns}

@@

	\vfill
	\onslide<6->{
	\begin{block}{Based on:}
		 \emph{ \small
			 M. , Ryvkin;
			\textbf{Multisymplectic observable reduction using constraint triples}; 
			\href{https://arxiv.org/abs/2506.00234}{arXiv:2506.00234}.
		 }.

	\end{block}
	}

@@

%-----------------------------------------------------------%
\begin{frame}[fragile]{Scope / Goals}
	\begin{block}{Upshots:}
		\begin{itemize}
			\item[$\bullet$] Observables $L_\infty$-algebra construction is purely algebraic!
			\begin{itemize}
				\item[$\cdot$] \emph{(It relies only on the \underline{standard Cartan calculus identities} for differential forms and vector fields.)}
			\end{itemize}\pause
			\item[$\bullet$] Possible generalization to \underline{BV-modules over a Gerstenhaber algebra!}
			\begin{itemize}
				\item[$\cdot$] \emph{(A suitably general framework to formalize Cartan calculus.)}
			\end{itemize}
		\end{itemize}
	\end{block}
	\pause \vfill

	\begin{block}{Claim:}
		To any given BV-module over a Gerstenhaber algebra together with a chosen closed element (a "cocycle") in the module, we can define:
		\begin{itemize}
			\item[$\cdot$] Hamiltonian pairs,
			\item[$\cdot$] together with an associated $L_\infty$-algebra structure.
		\end{itemize}
	\end{block}
	\pause \vfill

	\begin{block}{Applications:}
		\begin{itemize}
			\item[$\bullet$] A more conceptual picture for the algebraic reduction of the observables $L_\infty$-algebra in presence of constraints / symmetries.
		\end{itemize}
	\end{block}
	\vfill

>>>>

%----------------------------------------------------+
\begin{frame}[fragile]{Keywords}
\tikzstyle{every picture}+=[remember picture]
	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<5->{
			\tikz[baseline]{
		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
		            {The procedure to reduce the dimensions of Phase Space (e.g. of the space of measurable quantities) in presence of constraints or symmetries.};
			}
		}
	\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<4->{
			 \tikz[baseline]{
		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
		            {Higher analogue of DGLie algebras where Jacobi holds up to homotopies.};
			}
		}
	\end{column}
	\end{columns}

@@

	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<3->{
	 		 \tikz[baseline]{
	            \node[draw=green!40,anchor=base,text width=5cm] (s3)
	            {Algebraic object encoding measurable quantities of a mechanical system.};
	         }
		}		   	
		\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<2->{
				\tikz[baseline]{
	            \node[draw=red!40,anchor=base,text width=5cm] (s4)
	            {Algebraic object encoding Cartan Calculus.};
	           }	
			}
		\end{column}
	\end{columns}

@@

	\vfill
	\onslide<6->{
	\begin{block}{Based on:}
		\fullcite{ShortMiti2025}
	\end{block}
	}

@@

%-----------------------------------------------------------%
\begin{frame}[fragile]{Scope / Goals}
	\begin{upshotblocktitle}
		\begin{itemize}
			\item[$\bullet$] Observables $L_\infty$-algebra construction is purely algebraic!
			\begin{itemize}
				\item[$\cdot$] \emph{(It relies only on the \underline{standard Cartan calculus identities} for differential forms and vector fields.)}
			\end{itemize}\pause
			\item[$\bullet$] Possible generalization to \underline{BV-modules over a Gerstenhaber algebra!}
			\begin{itemize}
				\item[$\cdot$] \emph{(A suitably general framework to formalize Cartan calculus.)}
			\end{itemize}
		\end{itemize}
	\end{upshotblocktitle}
	\pause \vfill

	\begin{claimblocktitle}
		To any given BV-module over a Gerstenhaber algebra together with a chosen closed element (a "cocycle") in the module, we can define:
		\begin{itemize}
			\item[$\cdot$] Hamiltonian pairs,
			\item[$\cdot$] together with an associated $L_\infty$-algebra structure.
		\end{itemize}
	\end{claimblocktitle}
	\pause \vfill

	\begin{outlookblock}[Applications]
		A more conceptual picture for the algebraic reduction of the observables $L_\infty$-algebra in presence of constraints / symmetries.
	\end{outlookblock}
	\vfill

### 2025-10-23 bv-triples-main.tex
Slides complete.

%- T1tle P4g3 -------------------------------------------------------------------------------------------
\title{Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module} 
\subtitle{\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}}
\author[AMM]{
	\href{https://www.antoniomiti.it/}{Antonio Michele Miti}
	{\small joint work w/ Leonid Ryvkin}
}
\institute[SUR]{
	Sapienza Università di Roma \\
	Rome, Italy 	\\
	\vspace{.5em}
  \begin{tabular}[h]{ccc}
      \href{https://www.mat.uniroma1.it/en}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
      \href{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}{\includegraphics[width=3cm]{Logos/Civis_logo}}
  \end{tabular}    
}
\date[TorV25] % (optional, should be abbreviation of conference name)
{	
	{\vskip 1ex}
	Universit\'a di Roma - Tor Vergata, October 2025
}

@@

%+----------------------------------------------------------+
\section{BV-Modules: Algebraic Cartan Calculus}
%+----------------------------------------------------------+
	\checkpoint	
	\input{bv-triples-background}
%-----------------------------------------------------------%

%+----------------------------------------------------------+
\section{$L_\infty$ Algebra Associated with a BV-Module}
%+----------------------------------------------------------+
	\checkpoint	
	%\input{bv-triples-Rogers-generalized}
%-----------------------------------------------------------%

%+----------------------------------------------------------+
\section{An Application: Multisymplectic Reduction}
%+----------------------------------------------------------+
	\checkpoint	
	%\input{bv-triples-reduction}
%-----------------------------------------------------------%

%--------------------------------------------------------------------------------------------------%
	\addtocounter{framenumber}{-1}
		\begin{frame}{Conclusion:}
			\vfill
		  \centering 
		  \onslide<2->{\Huge\color{red} 
		  \emph{Thank you for your attention!}\normalsize \color{black}}
			\vfill
			%

		\end{frame}
		\note[itemize]{
			\item
		}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
% APPENDIX
%------------------------------------------------------------------------------------------------
\appendix
%------------------------------------------------------------------------------------------------
\section{Complementary Material}
	%\input{bv-triples-complementary-material}
	%\input{bv-triples-aknowledgements}
%------------------------------------------------------------------------------------------------

>>>>

%- T1tle P4g3 -------------------------------------------------------------------------------------------
\title{Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module} 
\subtitle{}
\author[AMM]{
	\href{https://www.antoniomiti.it/}{Antonio Michele Miti} \\
	{(\small joint work w/ \href{https://www.ryvkin.eu}{Leonid Ryvkin})}
}
\institute[SUR]{
	Sapienza Università di Roma \\
	Rome, Italy 	\\
	\vspace{.5em}
  \begin{tabular}[h]{ccc}
      \href{https://www.mat.uniroma1.it/en}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
      \href{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}{\includegraphics[width=3cm]{Logos/Civis_logo}}
  \end{tabular}    
}
\date[TorV25] % (optional, should be abbreviation of conference name)
{

	{\vskip 1ex}
	\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}
	\\
	Universit\'a di Roma - Tor Vergata, October 2025
}

@@

%+----------------------------------------------------------+
\section{BV-Modules: Algebraic Cartan Calculus}
%+----------------------------------------------------------+
	\input{bv-triples-background}
%-----------------------------------------------------------%

%+----------------------------------------------------------+
\section{$L_\infty$ Algebra Associated with a BV-Module}
%+----------------------------------------------------------+
	\input{bv-triples-Rogers-generalized}
%-----------------------------------------------------------%

%+----------------------------------------------------------+
\section{An Application: Multisymplectic Reduction}
%+----------------------------------------------------------+
	\input{bv-triples-reduction}
%-----------------------------------------------------------%

%--------------------------------------------------------------------------------------------------%
	\addtocounter{framenumber}{-1}
		\begin{frame}{Conclusions}
			\begin{upshotblocktitle}[Algebraic formalism for $L_\infty$ observables]
				We generalized Rogers' construction to constraint BV-modules.
			\end{upshotblocktitle}
			\vfill\pause

			\begin{upshotblocktitle}[Recovered previous reduction procedures]
				 Emploied this machinery to provide a conceptual framework for algebraic multisymplectic reduction of observables via constraint triples 
				 \smallskip

				 \fullcite{Blacker-M-Ryvkin-2024}\nocite{Blacker-M-Ryvkin-2024}
			\end{upshotblocktitle}
			\vfill\pause

			\begin{outlookblock}[An operadic reformulation]
				Rather than defining suitable constraint triples "by hand", it could be interesting to provide a systematic treatment, e.g. within the language of operads.
			\end{outlookblock}
			\vfill\pause

		  	\centering 
		  	{\Huge\color{red} 
		  	\emph{Thank you for your attention!}\normalsize \color{black}}
			\vfill
			%

		\end{frame}
		\note[itemize]{
			\item 				The constraint triples formalism provides a powerful tool to treat singular geometric (and algebraic) settings. 
		}
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------+
% APPENDIX
%-------------------------------------------------------+
%-------------------------------------------------------+
\appendix
%-------------------------------------------------------+
%-------------------------------------------------------+
\section{Complementary Material}
	\input{bv-triples-complementary-material}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\section{References \& Aknowledgements}
%------------------------------------------------------------------------------------------------
	\input{bv-triples-acknowledgements}

### 2025-10-23 bv-triples-reduction.tex
Slides complete.

%- D0cum3nt ----------------------------------------------------------------------------------------------
%\documentclass[beamer,10pt]{standalone}   
\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}[shrink]{Constraint $L_\infty$ Algebra Associated with a constraint BV-module}
	%
	\begin{defblock}[Constraint $L_\infty$-algebras] 
	A constraint vector space $L=\triple{L}$  equipped with a collection of constraint multilinear maps
	\begin{displaymath}
		l_j \colon L^{\otimes j} \to L[2-j]
	\end{displaymath}
	such that $(L_\Total, (l_j)_\Total)$ is an $L_\infty$-algebra.
	\end{defblock}
	\pause\vfill
	%

	Let $V$ a cons. BV-module over a cons. Gerst. algebra $G$,  $\omega\in V_\Wobs^{k+1}$ a cocycle.
	\begin{defblock}[Constraint vector space of Hamiltonian pairs]\label{def:constraint-algebraicham0}
		The	 constraint graded vector space:
		$$
		\Ham^0(V, \omega) := 
		\colvec{
			\big\{ (\alpha, X) \in V^{k-1}_\Total \oplus G_\Total^1 \mid \iota_X \omega = -\d\alpha \big\}
			\\
			\Ham^0(V, \omega) \cap \big(V_\Wobs \oplus G_\Wobs\big)
			\\
			\Ham^0(V, \omega) \cap \big( V_\Null \oplus G_\Null \big)
		}
		~.
		$$
	\end{defblock}
	\pause\vfill
	%

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Reduction Functor}
\begin{itemize}
  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
  \item Encodes reduced observables algebra.
  \item No need for regular quotient at geometric level.
\end{itemize}
\end{frame}
\note[itemize]{
	\item  
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Recovering Old Results}
\begin{itemize}
  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
  \item Explains residue defect in homotopy Jacobi identity.
  \item Matches geometric reduction under regularity.
\end{itemize}
\end{frame}
\note[itemize]{
	\item  This framework provides a unified approach to understanding various geometric and algebraic structures.
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

>>>>

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[beamer,10pt]{standalone}   
%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}[shrink]{Constraint $L_\infty$ Algebra Associated with a constraint BV-module}
	%
	\begin{defblock}[Constraint $L_\infty$-algebras] 
	A constraint vector space $L=\triple{L}$  equipped with \\
	a collection of constraint multilinear maps $l_j \colon L^{\otimes j} \to L[2-j]$\\
	such that $(L_\Total, (l_j)_\Total)$ is an $L_\infty$-algebra.
	\end{defblock}
	\pause\vfill
	%

	Let $V$ a cons. BV-module over a cons. Gerst. algebra $G$,  $\omega\in V_\Wobs^{k+1}$ a cocycle.
	\begin{defblock}[Constraint vector space of Hamiltonian pairs]\label{def:constraint-algebraicham0}
		The	 \emph{constraint ungraded vector space}:
		$$
		\Ham^0(V, \omega) := 
		\colvec{
			\big\{ (\alpha, X) \in V^{k-1}_\Total \oplus G_\Total^1 \mid \iota_X \omega = -\d\alpha \big\}
			\\
			\Ham^0(V, \omega) \cap \big(V_\Wobs \oplus G_\Wobs\big)
			\\
			\Ham^0(V, \omega) \cap \big( V_\Null \oplus G_\Null \big)
		}
		~.
		$$
	\end{defblock}
	\pause\vfill
	%

@@

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{Reduction Functor}

	\begin{remblock}[Reduction functor]\label{rk:red-functor}
		The very purpose of introducing categories of constraint objects is to assume the existence of a corresponding \emph{reduction functor} $\red$ that assigns to each constraint object its reduced counterpart.
	\end{remblock}
	\vfill\pause

	\begin{exblock}[Constraint associative algebras]
	A constraint associative algebra is equivalently given by a triple $A = \triple{A}$, where $A_\Wobs \subset A_\Total$ is a subalgebra, and $A_\Null \subset A_\Wobs$ is a (two-sided) ideal. i.e.:
		$$
			\red: \textbf{ConAlg} \to \textbf{Alg}~, \quad \mathcal A \mapsto \red(\mathcal A) := \mathcal A_\Wobs / \mathcal A_\Null~,
		$$
	\end{exblock}
	\vfill\pause

	\begin{upshotblocktitle}[Reduction functor for the $L_\infty$-algebra of observables]
		The $\Null$ part of $\Ham(V, \omega)$ is an $L_\infty$-ideal in the $\Wobs$ part. 
		\\
		Thus, the reduction functor applied to the constraint $L_\infty$-algebra of observables space gives a honest $L_\infty$-algebra.
	\end{upshotblocktitle}

\end{frame}
\note[itemize]{
	\item  	The reduction functor $\red$ assigns to each object $V$ the quotient vector space $\red(V) := V_\Wobs/V_\Null$, and to each morphism $f: V \to V'$ the induced map $\red(f): V_\Wobs/V_\Null \to V'_\Wobs/V'_\Null$.
